### 2021-07-11 docs/manuscript/manuscript.tex
remove trailing whitespaces

 The filters mentioned above are integrated in the following functions that
 evaluates the  quality of a given phenotype:

@@

>>>>

 The filters mentioned above are integrated in the following functions that
 evaluate the quality of a given phenotype:

@@

\paragraph*{S1 Appendix.}
\label{S1_Appendix}
{\bf Diffusion independent networks and robustness to changes in the signal input.}
